---
params: 
  sub_title:
    input: text
    label: Sub Title
    value: 'my_Sub_Title_and_File_Name'
title: 'Sierra Leone - Exploratory Data Analysis'
output: word_document
always_allow_html: true
data: 05/19/2022
knit: (
  function(inputFile, encoding) { 
  
    pSubTitle <- 'Sierra Leone health facility EDA'
  
    rmarkdown::render( 
      input       = inputFile, 
      encoding    = encoding, 
      params      = list(sub_title = pSubTitle),      
      output_file = pSubTitle) })
---


``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
rm(list=ls())

#import libraries
library(tidyverse)
library(readxl)
library(scales)
library(forcats)
library(scales)
library(forcats)
library(knitr)
library (sf)
library(DBI)
library(kableExtra)
library(tmap)
library(leaflet)
library(tools)

theme<-theme(plot.title=element_text(color="red",face="bold", size=13),
             plot.subtitle  = element_text(color="black",face="bold"),
             axis.text =element_text(color="grey7",face="bold",size=11),
             axis.title =element_text(color="grey7",face="bold",size=11),
             panel.border = element_rect(colour = "black", fill=NA, size=0.5),
             plot.caption=element_text(hjust = -0.01, face="italic", size=14),
             legend.key.height  = unit(0.2,"cm"),
             legend.key.width  = unit(0.4,"cm"),
             legend.spacing.x = unit(0.7, 'cm'),
             legend.position="bottom",
             #legend.justification = c("right", "bottom"),
             #legend.box.just = "",
             legend.margin = margin(15, 15, 15, 15),
             legend.text=element_text(size=11, face="bold"),
             legend.title = element_text( size=14, face='bold'),
             strip.text = element_text(size = 11, face='bold'))


###===INPUTS===###
input_table<-"D:/Grid3/GHFD/SLE/Digital Copy of DHIS2 Data_preprocessing2.xlsx"
admin1<-"District"
admin2<-"Chiefdom"
poi_var_name<-"Facility"
poi_var_type<-"Type"
lat_var<-"latitude"
long_var<-"longitude"
admin1_layer<-"D:/Grid3/GHFD/SLE/Sierra Leone Admins/Admin 2 District Shapefiles/Sierra_Leone_New_District_Shapefiles.shp"
admin2_layer<-"D:/Grid3/GHFD/SLE/Sierra Leone Admins/Admin 3 Chiefdom Shapefiles/Sierra_Leone_New_Chiefdom_Shapefiles.shp"
admin1_var<-"FIRST_New1"
admin2_var<-"New_Chief"


### PROCESS >> Do not edit below ###

# read data
input_table_type<-tools::file_ext(input_table)
if ( input_table_type=="xlsx"){
input_data<-read_excel(input_table) %>% mutate(lat=ifelse(!!rlang::sym(lat_var) == 0 , NA, !!rlang::sym(lat_var)),
                                               long=ifelse(!!rlang::sym(long_var) == 0 , NA, !!rlang::sym(long_var)))}
                                       
if ( input_table_type=="csv"){
input_data<-read_excel(input_table) %>% mutate(lat=ifelse(!!rlang::sym(lat_var) == 0 , NA, !!rlang::sym(lat_var)),
                                               long=ifelse(!!rlang::sym(long_var) == 0 , NA, !!rlang::sym(long_var)))}

# create admin1 and admin2 variabels if they are not exists in datasets as NA
if (!admin1 %in% names(input_data)){input_data<-input_data %>% mutate(admin1=NA)}
if (!admin2 %in% names(input_data)){input_data<-input_data %>% mutate(admin2=NA)}

# get only PoI  with lat/long
get_spatial<-input_data %>% filter(!is.na(lat)& !is.na(long) ) %>% 
  st_as_sf(coords = c("long", "lat"),crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")


# get input file names
input_table_name<-basename(input_table)
if (!is.na(admin1)){
  # get layer name
  admin1_layer_name<-basename(admin1_layer)
  # read admin1 layer
  admin1_bdry<-st_read(admin1_layer)
  # count hf points in admin 1 boundary
  admin1_poi_count<-st_join(admin1_bdry, get_spatial) %>% st_drop_geometry()%>% group_by(!!rlang::sym(admin1_var)) %>% summarize(p_count=n())
}else{admin1_layer_name<-"Admin1 attribute do not exist in the PoI table"}

if (!is.na(admin2)){
  # get layer name
  admin2_layer_name<-basename(admin2_layer)
  # read admin1 layer
  admin2_bdry<-st_read(admin2_layer)
  # count hf points in admin 1 boundary
  admin2_hf_count<-st_join(admin2_bdry, get_spatial) %>% st_drop_geometry()%>% group_by(!!rlang::sym(admin2_var)) %>% summarize(p_count=n())
}else{admin2_layer_name<-"Admin2 attribute do not exist in the PoI  table"}



```



# Objectives
+ Exploratory analysis of  **`r input_table_name`**


***

# Data inputs
+ PoI  : **`r input_table_name`** 
+ Admin 1 boundary: **`r admin1_layer_name`** 
+ Admin 2 boundary: **`r admin2_layer_name`** 
+ Admin 1 field in PoI table : **`r admin1`** 
+ Admin 2 field in PoI table : **`r admin2`** 
+ PoI name field in PoI table : **`r poi_var_name`** 
+ PoI type 2 field in PoI table : **`r poi_var_type`** 

***


``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
#get count of na rows in admin columns and facility name column
admin1_na<-input_data %>% filter(is.na(admin1))
admin2_na<-input_data %>% filter(is.na(admin2))
fname_na<-input_data %>% filter(is.na(!!rlang::sym(poi_var_name)))
# get count of rows that have only numeric values in admin columns and facility name column
admin1_num_only<-input_data %>% filter(str_detect(admin1,"^[:digit:]+$")==TRUE )
admin2_num_only<-input_data %>% filter(str_detect(admin2,"^[:digit:]+$")==TRUE )
fname_num_only<-input_data %>% filter(str_detect(!!rlang::sym(poi_var_name),"^[:digit:]+$")==TRUE )
if ("type" %in% names(input_data)){type_count<-length(input_data %>% pull(type) %>% unique())} else{type_count<-0}
sub_type_count<-length(input_data %>% pull(sub_type) %>% unique())
```

## PoI  table summary:

+ There are **`r ncol(input_data)`** columns in input dataset.
+ There are **`r nrow(input_data)`** rows in input dataset.
+ admin1 variable has **`r nrow(admin1_na)`** NA records. 
+ admin2 variable has **`r nrow(admin2_na)`** NA records. 
+ facility_name variable has **`r nrow(fname_na)`** NA records.
+ admin1 variable has **`r nrow(admin1_num_only)`** records with only numerical values. 
+ admin2 variable has **`r nrow(admin2_num_only)`** records with only numerical values. 
+ facility_name variable has **`r nrow(fname_num_only)`** records with only numerical values. 
+ There are  **`r type_count`** facility types in the facility table. 
+ There are  **`r sub_type_count`** facility  sub_types in the facility table. 
<br>

***

### Input PoI  locations:
+ The map below shows PoI  points that have lat/long. PoI  are color coded based on facility type (sub_type)

<br>

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}
tmap_mode('view') 
tm_basemap(leaflet::providers$Esri.WorldImagery)+
tmap::tm_shape(get_spatial) +
tm_dots("sub_type",palette="-RdYlBu",id="something",
  popup.vars=c("admin1"=admin1, "admin2"=admin2,"PoI name"=poi_var_name ))

```

<br>

### Summary of PoI  points by location(lat/long)
+ Some of the PoI  do not have geospatial locations.The plot below summarizes facility data based on lat/long attribute information. 

***
      
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

  summary_by_lat_long<-input_data %>%  
    mutate(has_latlong=case_when(!is.na(lat)~ "With lat/long",TRUE ~ as.character("No lat/long"))) %>% 
  group_by(has_latlong) %>% summarise(Count=n()) %>%
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))  
  ymax<-summary_by_lat_long %>% pull(Count) %>% max()
  summary_by_lat_long_p<-summary_by_lat_long %>% 
  ggplot( aes(x=has_latlong,y=Count, fill=has_latlong))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
  theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
   summary_by_lat_long_p
    ```  
<br>

### Summary of duplicate PoI :
+ The table below flags duplicated PoI  if there are any. 
+ PoI  with the same admin1, admin2 and facility_name are assumed to be duplicated.

<br>

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=5, fig.width=15}

summary_by_duplicates<-input_data %>%filter(poi_uuid_isUnique==1) %>% 
  select(admin1, admin2,poi_var_name) %>% arrange(desc(poi_var_name))
if(nrow(summary_by_duplicates)>=1){
 summary_by_duplicates %>% kbl() %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))}
if(nrow(summary_by_duplicates)==0){
 print("There are no duplicated facilites in the input table")}

```

<br>

### Summary of PoI  points by admin1:
+ Table below summarizes facility count by admin1 attributes. We expect the facility count between admin1 units to be similar.

<br>

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=5, fig.width=15}
if (!is.na(admin1)){

summary_by_admin1<-input_data %>% mutate( admin1=as.factor(!!rlang::sym(admin1))) %>% 
count(admin1) %>% arrange(desc(n)) %>%  mutate( prc=paste0("% ",round((n/nrow(input_data)*100),1))) %>% 
 kbl() %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
summary_by_admin1}else{print("Admin1 attribute does not exist in the PoI  table")}
```


<br>

### Summary of PoI  points by admin1 boundary:
+ Table below summarizes facility count by admin1 boundary. We expect the facility count for the admin1 boundary to be similar to the table above. If not, some PoI  may be missing lat/long, the points are in the wrong location, or the boundary is wrong. 

<br>

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=5, fig.width=15}
if (!is.na(admin1)){

summary_by_admin1_bdry<-admin1_poi_count %>% mutate(admin1=as.factor(!!rlang::sym(admin1_var))) %>% 
arrange(desc(p_count)) %>%  mutate( prc=paste0("% ",round((p_count/nrow(input_data)*100),1))) %>% 
select(admin1, n=p_count,prc) %>% 
 kbl()  %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
summary_by_admin1_bdry}else{print("Admin1 attribute do not exist in the PoI  table")}
```




<br>

***

### Summary of PoI  points by admin2:
+ Table below summarizes facility count by admin2 attributes. We expect the facility count between admin2 units to be similar.

<br>
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=5, fig.width=15}

if (!is.na(admin1)){
summary_by_admin2<-input_data %>% mutate(admin2=as.factor(!!rlang::sym(admin2)),admin1=as.factor(!!rlang::sym(admin1))) %>% 
count(admin1,admin2) %>% arrange(admin2) %>%  mutate( prc=paste0("% ",round((n/nrow(input_data)*100),1))) %>%  
 kbl() %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
summary_by_admin2}else{print("Admin2 attribute does not exist in the PoI  table")}
```
 
 
<br>

### Summary of PoI  points by admin2 boundary:
+ Table below summarizes facility count by admin2 boundary. We expect the facility count for the admin2 boundary to be similar to the table above. If not, some PoI  may be missing lat/long, the points are in the wrong location, or the boundary is wrong.

<br>

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=5, fig.width=15}

if (!is.na(admin2)){
summary_by_admin2_bdry<-admin2_hf_count %>% mutate(admin2=as.factor(!!rlang::sym(admin2_var))) %>% 
arrange(desc(p_count)) %>%  mutate( prc=paste0("% ",round((p_count/nrow(input_data)*100),1))) %>% 
select(admin2, n=p_count,prc) %>% 
 kbl()  %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
summary_by_admin2_bdry}else{print("Admin2 attribute does not exist in the PoI  table")}
```

 <br>
 

*** 
### Summary of PoI  points by sub_type:
+ The table below summarizes facility types based on sub_type. sub_type are the facility types derived from facility names. Make corrections in the facility table if there are spelling issues or types that do not make sense.

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=15}
summary_by_sub_type<-input_data %>% mutate(sub_type=as.factor(sub_type)) %>% 
count(sub_type) %>%  arrange(desc(n)) %>%  mutate(prc=paste0("% ",round((n/nrow(input_data)*100),1))) %>% 
 kbl() %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
summary_by_sub_type
    ```
 <br>
 

*** 
### Summary of PoI  points by type:
+ The table below summarizes facility types based on the type column. These are the original facility types.

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=15}

if (!is.na(poi_var_type)){
summary_by_type<-input_data %>% mutate(type=as.factor(!!rlang::sym(poi_var_type))) %>% 
count(type) %>%  arrange(desc(n)) %>%  mutate(prc=paste0("% ",round((n/nrow(input_data)*100),1))) %>% 
 kbl() %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
summary_by_type}else{print("Original facility type attribute does not exist in the PoI  table")}
    ```
 <br>
 

*** 
### PoI  types: Type versus sub_type:
+ The table below maps type (original type) column with sub_type (type extracted from facility name) column.
Please go over the types that were mapped incorrectly.

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=15}

if (!is.na(poi_var_type)){
type_to_sub_type<-input_data %>% group_by(!!rlang::sym(poi_var_type), sub_type) %>% summarise(Count=n()) %>% 
kbl() %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
type_to_sub_type}else{print("Original facility type attribute does not exist in the PoI  table")}
    ```

*** 

## Initial Quality Check

<br>

***

<br>

### Summary by Settlement extent

+ We expect PoI  to fall on a settlement extent. The plot below summarizes facility by settlement extent type in which the PoI  are located.
+ *Out of a settlement* indicates PoI  that more than 250 meters from a settlement extent. Either these PoI  do not have the right lat/long attribute or the settlement extent layer that we use missed some settlements. 
           
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=10, fig.width=12}
input_data<-input_data %>% mutate(settlement_type=case_when(settlement_type=="Built-Up Area" ~ "bua",settlement_type=="Built-up Area" ~ "bua",
                                                            settlement_type=="Small Settlement Area" ~ "ssa",
                                                            settlement_type=="Hamlet" ~ "hamlet",
                                                            TRUE ~ as.character(settlement_type))) 
input_data $settlement_type <- factor(input_data$settlement_type, levels = c("bua", "ssa", "hamlet", "Out of a settlement"))
  summary_by_settlement_extent<-input_data %>% filter(!is.na(lat)) %>% 
  group_by( settlement_type) %>% summarise(Count=n()) %>%
  mutate(percent = prop.table(Count), prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))  
  ymax<-summary_by_settlement_extent %>% pull(Count) %>% max()
    summary_by_settlement_extent_p<- summary_by_settlement_extent %>% 
    ggplot( aes(x=settlement_type,y=Count, fill=settlement_type))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
  theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_settlement_extent_p
 
 ``` 
 
 <br>
   
### PoI  points with distance to settlement extent
  + The map below shows faciliites that far from a settlement extent by distance.
 
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE,fig.height=7, fig.width=12}

distance_to_sett_extent<-get_spatial %>% mutate(dist_to_settlement_type = replace_na(dist_to_settlement_type, 250))%>% 
    mutate(dist_to_settlement =cut(dist_to_settlement_type , breaks=c(-Inf,0, 50,100,249, Inf), 
                      labels=c("on a settlement","<=50m","<=100m","<=250", "250m >"))) 
 
 tmap_mode('view') 
tm_basemap(leaflet::providers$Esri.WorldImagery)+
tmap::tm_shape(distance_to_sett_extent) +
tm_dots("dist_to_settlement",palette="-RdYlBu",id="something",
  popup.vars=c("admin1"=admin1, "admin2"=admin2,"PoI name"=poi_var_name ))

```
 
 
<br>

*** 

### Summary by Overlaps
+ Sometimes more than one facility shares the same lat/long. The plot below shows the PoI  with the same lat/long. 

<br>       
  ``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

  summary_by_overlapes<-input_data %>%  filter(!is.na(lat)) %>% select(is_overlap) %>% 
    mutate(is_overlap2=case_when(is_overlap=="YES" ~ "Overlap",is_overlap=="NO" ~  "Non-Overlap")) %>% 
  group_by( is_overlap2) %>% summarise(Count=n()) %>%
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))  
  ymax<-summary_by_overlapes %>% pull(Count) %>% max()
  summary_by_overlapes_p<-summary_by_overlapes %>% 
  ggplot( aes(x=is_overlap2,y=Count, fill=is_overlap2))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
  theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_overlapes_p
    ```      

<br>

*** 

### Summary by admin1 and  admin2 names match

+ We expect admin names from the facility table to match admin names from the admin boundaries. The plot below summarizes the results from matching the admin names between the PoI  table and the boundary. A Fuzzy match method is used to match admin names.NA values in admin2 match result (right plot) shows admin2 names that admin1 did not matched.If admin1 names did not match, admin2 names assume to be not  matched.

<br> 
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

if (!is.na(admin1) & !is.na(admin2)){
  summary_by_admin1_match<-input_data %>%   select(admin1_names_match=admin1_clean_match_result,admin2_names_match=admin2_clean_match_result) %>% 
  group_by( admin1_names_match,admin2_names_match) %>% summarise(Count=n()) %>%gather(key, value, -Count) %>% 
    group_by(key, value) %>% summarise(Count=sum(Count)) %>% 
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<-summary_by_admin1_match %>% pull(Count) %>% max()
summary_by_admin1_match_p<-summary_by_admin1_match %>% 
  ggplot( aes(x=value,y=Count, fill=value))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
  facet_grid(.~key)+ theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
summary_by_admin1_match_p
}else if ( !is.na(admin1)) {summary_by_admin1_match<-input_data %>%   select(admin1_names_match=admin1_clean_match_result) %>% 
  group_by( admin1_names_match) %>% summarise(Count=n()) %>%gather(key, value, -Count) %>% 
    group_by(key, value) %>% summarise(Count=sum(Count)) %>% 
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<-summary_by_admin1_match %>% pull(Count) %>% max()
summary_by_admin1_match_p<-summary_by_admin1_match %>% 
  ggplot( aes(x=value,y=Count, fill=value))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record", title="Admin1")+
   theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
summary_by_admin1_match_p
}else if ( !is.na(admin1)) {summary_by_admin2_match<-input_data %>%   select(admin2_names_match=admin2_clean_match_result) %>% 
  group_by( admin2_names_match) %>% summarise(Count=n()) %>%gather(key, value, -Count) %>% 
    group_by(key, value) %>% summarise(Count=sum(Count)) %>% 
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<-summary_by_admin1_match %>% pull(Count) %>% max()
summary_by_admin2_match_p<-summary_by_admin2_match %>% 
  ggplot( aes(x=value,y=Count, fill=value))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record", title="Admin2")+
   theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
summary_by_admin2_match_p}else{print("Admin1 and Admin2 attributes do not exist in the PoI table")}



    ``` 
    
 
<br>

*** 

### Admin1 names that did not matched
+ We expect admin names from the facility table to match admin names from admin boundaries. Admin1 names that did not matched between PoI  and admin1 boundary are listed below. We used a fuzzy match method to matched admin1 names. Please check unmatched names below and confirm the match process.

<br> 

+ Unmatched admin1 names from **PoI ** table:
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

if (!is.na(admin1)){
admin1_not_matched_from_hf<-input_data %>%filter(admin1_clean_match_result=="NO") %>% pull(admin1_clean_updated) %>% unique()

if (length(admin1_not_matched_from_hf)==0){print ("There is no unmatched admin1 names from PoItable")} else{print(admin1_not_matched_from_hf)}}else{print("Admin1 attributes do not exist in the PoI table")}

    ```   


<br> 

+ Unmatched admin1 names from **admn 1 boundary** layer:These admin units may not have any facility points
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}
if (!is.na(admin1) ){
admin1_matched_from_hf<-input_data %>%filter(admin1_clean_match_result=="YES") %>% pull(admin1_clean_updated) %>% unique()
bndry_unmatched_admin1<-admin1_bdry %>% filter(!admin1_bry %in% admin1_matched_from_hf ) %>% pull(admin1_bry)%>% unique()
if (length(bndry_unmatched_admin1)==0){print ("There is no unmatched admin1 names from admin1 boundary")} else{print(bndry_unmatched_admin1)
  }}else{print("Admin1 attributes do not exist in the PoI table")}
    ```   

<br>

*** 

### Admin2 names that did not matched
+ We expect admin names from facility table to match admin names from admin boundaries. Admin2 names that 
did not matched between PoI  and admin2 boundary listed below. We used fuzzy match method to to matched admin2 names. 
Please check unmatched names below and confirm the match process.

<br> 

+ Unmatched admin2 names from **PoI ** table:
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

if (!is.na(admin2) ){
admin2_not_matched_from_hf<-input_data %>%filter(admin2_clean_match_result=="NO") %>% pull(admin2_clean_updated) %>% unique()
if (length(admin2_not_matched_from_hf)==0){print ("There is no unmatched admin1 names from PoI table")} else{print(admin2_not_matched_from_hf)
}}else{print("Admin2 attributes do not exist in the PoI table")}
    ```   
 
 <br> 

+ Unmatched admin2 names from **admn 2 boundary** layer: These admin units may not have any facility points
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}
if (!is.na(admin2)){
admin2_not_matched_from_hf<-input_data %>%filter(admin2_clean_match_result=="YES") %>% pull(admin2_clean_updated) %>% unique()
bndry_unmatched_admin2<-admin2_bdry %>% filter(!admin2_bry %in% admin2_not_matched_from_hf)  %>% 
  pull(admin2_bry)%>% unique()
if (length(bndry_unmatched_admin2)==0){print ("There is no unmatched admin1 names from admin1 boundary")} else{print(bndry_unmatched_admin2)
  }}else{print("Admin2 attributes do not exist in the PoItable")}
```
     
    
<br>

*** 

### Summary by admin1 and admin2 boundary name match

<br> 
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}
if (!is.na(admin1) & !is.na(admin2)){
  summary_by_admin1_bdry_match<-input_data %>% filter(!is.na(lat)) %>% 
  select(admin1_bdry_names_match=admin1_bryMatch,admin2_bdry_names_match=admin2_bryMatch) %>% 
  group_by( admin1_bdry_names_match,admin2_bdry_names_match) %>% summarise(Count=n()) %>%gather(key, value, -Count) %>% 
    group_by(key, value) %>% summarise(Count=sum(Count)) %>% 
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<- summary_by_admin1_bdry_match%>% pull(Count) %>% max()
 summary_by_admin1_bdry_match_p<- summary_by_admin1_bdry_match %>% 
  ggplot( aes(x=value,y=Count, fill=value))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
  facet_grid(.~key)+ theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_admin1_bdry_match_p}else if(!is.na(admin1)){
   
 summary_by_admin1_bdry_match<-input_data %>% filter(!is.na(lat)) %>% 
  select(admin1_bdry_names_match=admin1_bryMatch) %>% 
  group_by( admin1_bdry_names_match) %>% summarise(Count=n()) %>%gather(key, value, -Count) %>% 
    group_by(key, value) %>% summarise(Count=sum(Count)) %>% 
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<- summary_by_admin1_bdry_match%>% pull(Count) %>% max()
 summary_by_admin1_bdry_match_p<- summary_by_admin1_bdry_match %>% 
  ggplot( aes(x=value,y=Count, fill=value))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record", title="Admin1")+
 theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_admin1_bdry_match_p}else if ( !is.na(admin2)) {
   summary_by_admin1_bdry_match<-input_data %>% filter(!is.na(lat)) %>% 
  select(admin2_bdry_names_match=admin2_bryMatch) %>% 
  group_by(admin2_bdry_names_match) %>% summarise(Count=n()) %>%gather(key, value, -Count) %>% 
    group_by(key, value) %>% summarise(Count=sum(Count)) %>% 
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<- summary_by_admin1_bdry_match%>% pull(Count) %>% max()
 summary_by_admin1_bdry_match_p<- summary_by_admin1_bdry_match %>% 
  ggplot( aes(x=value,y=Count, fill=value))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record", title="Admin2")+
   theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_admin1_bdry_match_p}else{print("Admin1 and Admin2 attributes do not exist in the PoI table")}
   
    ``` 
    
    
     
<br>

*** 

### Summary by distance to admin1 boundary if boundary are not matched

+ We expect PoI  to fall into the respective admin1 boundaries. However, sometimes facility do not fall into respective admin1 boundaries. These PoI  may have the wrong lat/long or the boundaries are incorrect. NA values indicates PoI  where their admin1 names did not match the admin1 names from admin boundary

<br> 
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

if (!is.na(admin1)){
  check<-input_data %>% filter(admin1_bryMatch=="NO" ) %>%nrow()
  if (check>1){
  summary_by_dist_admin1_bdry_match<-input_data %>% filter(!is.na(lat)) %>%
  filter(admin1_bryMatch=="NO" ) %>% 
  select(dist_to_admin1_bry_border_km ) %>% 
  mutate(distance=cut(dist_to_admin1_bry_border_km, breaks=c(-Inf, 1, 2,5,10,25, Inf), 
                      labels=c("<=1km","1-2km","2-5km","5-10km","10-25km", "25km >"))) %>% 
  group_by( distance) %>% summarise(Count=n()) %>%
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<- summary_by_dist_admin1_bdry_match%>% pull(Count) %>% max()
 summary_by_dist_admin1_bdry_match_p<- summary_by_dist_admin1_bdry_match %>% 
  ggplot( aes(x=distance,y=Count, fill=distance))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
   theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_dist_admin1_bdry_match_p }else{print("All facility points fall in right admin1 boundary")}
  }else{print("Admin1 attributes do not exist in the PoI table")}

  
   
    ```    
   <br>

***

### PoI  that do not fall right admin1 boundary
+ The map below shows the PoI  that do not fall into the respective admin1 boundary. As shown on the map, some of the PoI  fall very close to the correct admin boundary. We need to confirm that these PoI  in the right location or if the boundary is incorrect. However for the PoI  that fall very far from the respective boundary, we need to make sure the facility locations are correct. If the facility locations are correct we need change admin1 attribute for these PoI .

<br>

``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

if (!is.na(admin1)){if (check>1){
all_points_<-get_spatial %>% filter(admin1_bryMatch=="NO" ) %>%filter(!is.na(dist_to_admin1_bry_border_km) ) %>%
   mutate(dist_to_admin1_bry_border_km=cut(dist_to_admin1_bry_border_km, breaks=c(-Inf, 1, 2,5,10,25, Inf), 
                      labels=c("<=1km","1-2km","2-5km","5-10km","10-25km", "25km >")))
tmap_mode('view') 
map<-tm_basemap(leaflet::providers$Esri.WorldImagery)+
tmap::tm_shape(admin1_bdry) +tm_polygons(admin1_var, legend.show = F) +
  tm_text(admin1_var, size = 1)+
  tm_borders("black")+
  tm_shape(all_points_)+tm_dots("dist_to_admin1_bry_border_km",palette="-RdYlBu",id="something",
  popup.vars=c("admin1"=admin1, "admin2"=admin2,"PoI name"=poi_var_name ))
map}else{
  print("All facility points fall in right admin1 boundary")}
}else{print("Admin1 attributes do not exist in the PoI table")}
``` 
<br>

*** 

### Summary by distance to admin2 boundary if boundary are not matched
+ We expect PoI  to fall into the respective admin2 boundaries. However, sometimes facility do not fall into respective admin2 boundaries. These PoI  may have the wrong lat/long or the boundaries are incorrect. NA values indicates PoI  where their admin2 names did not match the admin2 names from admin boundary. We can not check if a facility falls into right admin2 boundary because their admin names did not matched any admin2 names from admin2 boundary.

<br> 
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

if (!is.na(admin2)){
  check<-input_data %>% filter(admin2_bryMatch=="NO" ) %>%nrow()
  if (check>1){
  summary_by_dist_admin2_bdry_match<-input_data %>% filter(!is.na(lat)) %>%
  filter(admin2_bryMatch=="NO" ) %>% 
  select(dist_to_admin2_bry_border_km ) %>% 
  mutate(distance=cut(dist_to_admin2_bry_border_km, breaks=c(-Inf, 1, 2,5,10,25, Inf), 
                      labels=c("<=1km","1-2km","2-5km","5-10km","10-25km", "25km >"))) %>% 
  group_by( distance) %>% summarise(Count=n()) %>%
  mutate(percent = prop.table(Count),  prc=paste0( "%",round(percent*100, 1),"\n(", Count,")"))

  ymax<- summary_by_dist_admin2_bdry_match%>% pull(Count) %>% max()
 summary_by_dist_admin2_bdry_match_p<- summary_by_dist_admin2_bdry_match %>% 
  ggplot( aes(x=distance,y=Count, fill=distance))+
   geom_bar(stat="identity")+
  geom_text(aes(label = prc),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
   theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_dist_admin2_bdry_match_p}else{
  print("All  fall in right admin2 boundary")}
}else{print("Admin2 attributes do not exist in the PoI table")}
    ```  
   <br>

***

### PoI  that do not fall into right admin2 boundary
+ The map below shows the PoI  that do not fall into the respective admin2 boundary. As shown on the map, some of the PoI  fall very close to the correct admin boundary. We need to confirm that these PoI  in the right location or if the boundary is incorrect. However for the PoI  that fall very far from the respective boundary, we need to make sure the facility locations are correct. If the facility locations are correct we need change admin2 attribute for these PoI .
***
<br>
***
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}
if (!is.na(admin2)){if (check>1){
all_points_<-get_spatial %>% filter(admin2_bryMatch=="NO" ) %>% filter(!is.na(dist_to_admin2_bry_border_km) ) %>%
   mutate(dist_to_admin2_bry_border_km=cut(dist_to_admin2_bry_border_km, breaks=c(-Inf, 1, 2,5,10,25, Inf), 
                      labels=c("<=1km","1-2km","2-5km","5-10km","10-25km", "25km >")))
tmap_mode('view') 
map<-tm_basemap(leaflet::providers$Esri.WorldImagery)+
tmap::tm_shape(admin2_bdry) +tm_polygons(admin2_var, legend.show = F) +
  tm_text(admin2_var, size = 1)+
  tm_borders("black")+
  tm_shape(all_points_)+tm_dots("dist_to_admin2_bry_border_km",palette="-RdYlBu",id="something",
  popup.vars=c("admin1"=admin1, "admin2"=admin2,"PoI name"=poi_var_name ))
map}else{
  print("All  points fall in right admin2 boundary")}
}else{print("Admin2 attributes do not exist in the PoI table")}

```


<br>

*** 

### Check if points are clusterded in 25 and 50 meter distance

+ Event though some PoI  can be located in the same building or compound, we should not see PoI  very close to each other, especially in rural areas. The plot below summarizes PoI  based on 25 and 50 meter clusters.

<br> 
``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}

  summary_by_cluster<-input_data %>% filter(!is.na(lat)) %>%
  select(points_in_25m=geo_dbscan_r25_cluster_id,points_in_50m=geo_dbscan_r50_cluster_id) %>%
  gather(key, value) %>% filter(value>0) %>% 
  group_by( key) %>% summarise(Count=n())

  ymax<- summary_by_cluster %>% pull(Count) %>% max()
 summary_by_cluster_p<- summary_by_cluster %>% 
  ggplot( aes(x=key,y=Count, fill=key))+
   geom_bar(stat="identity")+
  geom_text(aes(label = Count),
    position = position_dodge(0.9),
    vjust = -0.5)+ylim(0, ymax+((10*ymax)/100))+
  guides(fill=FALSE)+labs(x="",y="Count of record")+
   theme+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
 summary_by_cluster_p
    ```  
   <br>

***

### PoI  that have less than 50m to each other
The map shows PoI  that have less than 50 meters between each other.


<br>


``` {r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE,fig.height=7, fig.width=12}


cluster_50m<-get_spatial %>% filter(geo_dbscan_r50_cluster_id>0)

 
tmap_mode('view') 
map<-tm_basemap(leaflet::providers$Esri.WorldImagery)+
tmap::tm_shape(cluster_50m)+tm_dots("red",id="something",
  popup.vars=c("admin1"=admin1, "admin2"=admin2,"PoI name"=poi_var_name ))
map

```
